### 2016-06-30 ch02-qlogms/excitation-design.tex
Define robustness

\subsection{General Purpose Robust Excitation Signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is, however, not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

>>>>

\subsection{General Purpose Robust Excitation Signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is, however, not necessary to know how many resonances are in the system and at what precise frequencies those may occur.
In short, we consider an input signal to be \term{robust}, if such signal allows one to measure the \gls{FRF} of a wide variety of systems well, without requiring a lot of specific prior information regarding the system.
Moreover, a robust input signal should not be very sensitive towards assumptions regarding the system under test (or should be easily adaptable if the assumptions are only approximately valid).
